Optimal (Multiway) Spatial Joins

### 2024-05-28 msj.tex
yufei

\extraspacing {\underline{\em Example 5.3.}} Consider the tuples $\bm{t}_1$, $\bm{t}_2$, and $\bm{t}_3$ of $ \J(R_1, H', V)$ given in Example 5.2. For $\bm{t}_1 = (\alpha, h_2', v_1)$, its effective horizontal segment is $\texttt{DC}$ (see Figure~\ref{fig:hv:type2:ex}b). For $\bm{t}_2 = (\alpha, h_3', v_1)$, its effective horizontal segment is \texttt{EB}. For $\bm{t}_3 = (\alpha, h_3', v_2) \in \J(R_1, H', V)$, its effective horizontal segment is \texttt{EA}. Accordingly, as can be seen from Figure~\ref{fig:hv:type2:ex}c,
$\contained_{R_{k-2}}(\bm{t}_1) = \contained_{R_2}(\bm{t}_1) = \set{\beta_1}$, $\contained_{R_2}(\bm{t}_2) = \set{\beta_1, \beta_2, \beta_3}$, and $\contained_{R_2}(\bm{t}_2) = \set{\beta_3}$.
\qed

@@

\yf{example}

>>>>

\extraspacing {\underline{\em Example 5.3.}} Consider the tuples $\bm{t}_1$, $\bm{t}_2$, and $\bm{t}_3$ of $ \J(R_1, H', V)$ given in Example 5.2. For $\bm{t}_1 = (\alpha, h_2', v_1)$, its effective horizontal segment is $\texttt{DC}$ (see Figure~\ref{fig:hv:type2:ex}b). For $\bm{t}_2 = (\alpha, h_3', v_1)$, its effective horizontal segment is \texttt{EB}. For $\bm{t}_3 = (\alpha, h_3', v_2) \in \J(R_1, H', V)$, its effective horizontal segment is \texttt{EA}. Accordingly, as can be seen from Figure~\ref{fig:hv:type2:ex}c,
$\contained_{R_{k-2}}(\bm{t}_1) = \contained_{R_2}(\bm{t}_1) = \set{\beta_1}$, $\contained_{R_2}(\bm{t}_2) = \set{\beta_1, \beta_2, \beta_3}$, and $\contained_{R_2}(\bm{t}_3) = \set{\beta_3}$.
\qed

@@

\extraspacing {\underline{\em Example 5.6.}} It is clear from Figure~\ref{fig:hv:type2:ex}(d) that $\contained_{R_2}(h_3^*)$ has rectangles $\beta_3, \beta_2$, $\beta_1$, sorted in descending order of their right boundaries' x-coordinates. Consider $\bm{t}_2 = (\alpha, h_3', v_1)$ and $\bm{t}_3 = (\alpha, h_3', v_2)$. Segment $h_3^*$ is the minimal segment of $h_3'$. As stated in Lemma~\ref{lmm:hv:type2:contained-h*}, both $\contained_{R_2}(\bm{t}_2) = \set{\beta_1, \beta_2, \beta_3}$ and $\contained_{R_2}(\bm{t}_3) = \set{\beta_1}$ are prefixes of the sorted order of $\contained_{R_2}(h_3^*)$. Regarding $h_2^*$, it is the minimal segment of $h_2'$, and $\contained_{R_2}(h_2^*)$ contains only  $\beta_1$. For $\bm{t}_1 = (\alpha, h_2', v_1)$, $\contained_{R_2}(\bm{t}_1) = \set{\beta_1}$ is a (trivial) prefix of $\contained_{R_2}(h_2^*)$, as is consistent with the lemma.
\qed
